Paper Summaries

### 2019-06-06 Report/Progress_Report/Background.tex
Finished section on data generation

\pagenumbering{arabic}
\setcounter{page}{1}

@@

\subsection{Audio Driven Data Generation}

\subsubsection{Imperial}
\cite{Tzirakis2019}

\subsubsection{VOCA}
The VOCA model \cite{Cudeiro2019} synthesises video sequences of 3D models speaking given an audio input.
The VOCASET dataset discussed in section \ref{3D Datasets}, was captured with the intention of training this model to be independent of the speaker, hence a large range of speakers are used within the dataset.
The model is comprised of three sections: audio feature extraction, a feature encoder and a decoder to drive a template facial mesh from the FLAME model \cite{Li2017}.
The audio feature extraction makes use of the pre-trained Mozilla implementation of the DeepSpeech model, based on the paper by Hannun et al. \cite{Hannun2014}.
The DeepSpeech model takes audio as an input and returns the unnormalised log-probabilities for an alphabet of the 26 standard characters, a space, apostrophe and blank character for time slices in the audio input.
The encoder is a convolutional network which is conditioned on the speakers identity, such that the latent space of speaker styles can later be explored on new audio inputs.
Finally, the decoder is made up of a fully connected layer with a linear activation function is used to output the displacements of the 5023 vertices in the template face.

\subsubsection{Nvidia}
\cite{Karras2017a}

@@

\section{Recurrent Models}
\begin{itemize}
    \item Recurrent networks
    \item LSTMs
    \item Attention Mechanism
\end{itemize}

\section{Speech Recognition}
Deep Speech \cite{Karras2017a}

>>>>

\pagenumbering{arabic}
\setcounter{page}{1}
\frenchspacing

@@

\subsection{Audio Driven Data Generation}
Karras et al proposed a method for generating 3D facial animation from audio with the use of a CNN architecture \cite{Karras2017a}.
The model is actor specific, but is only trained on 3-5 minutes of data of the actor.
Short range temporal features are first extracted from the audio by a formant analysis network.
This representation is then analysed by an articulation network which also accepts a learned emotional state of the speaker.
The output layer drives displacements from a neutral 3d mesh of the actor.

However, as the model by Karras et al. is not independent of the actor it cannot generalise to new subjects.
Tzirakis et al. propose a model which is independent of speaker and capture rig \cite{Tzirakis2019}.
As discussed in section \ref{3D Datasets}, a dataset was constructed of 3D speaking faces using the LRW dataset \cite{Chung2016} for the corpus.
This allowed Tzirakis et al. to create a model which can synthesise facial motion from audio from the LRW dataset.
The model used is similar to that used in \cite{Karras2017a}, firstly extracting short term temporal features from the input audio with a convolutional network followed by another convolutional network to analyse the extracted features.
Unlike the model used in \cite{Karras2017a}, the model used in \cite{Tzirakis2019} is trained to drive learnt blendshapes.
This reduces the number of output parameters of the model substantially in comparison to that used by Karras et al.

Similar to \cite{Tzirakis2019}, the VOCA model \cite{Cudeiro2019} synthesises video sequences of 3D models speaking given an audio input.
The VOCASET dataset discussed in section \ref{3D Datasets}, was captured with the intention of training this model to be independent of the speaker, hence a large range of speakers are used within the dataset.
The model is comprised of three sections: audio feature extraction, a feature encoder and a decoder to drive a template facial mesh from the FLAME model \cite{Li2017}.
The audio feature extraction makes use of the pre-trained Mozilla implementation of the DeepSpeech model, based on the paper by Hannun et al. \cite{Hannun2014}.
The DeepSpeech model takes audio as an input and returns the unnormalised log-probabilities for an alphabet of the 26 standard characters, a space, apostrophe and blank character for time slices in the audio input.
The encoder is a convolutional network which is conditioned on the speakers identity, such that the latent space of speaker styles can later be explored on new audio inputs.
Finally, the decoder is made up of a fully connected layer with a linear activation function is used to output the displacements of the 5023 vertices in the template face.

@@

To the best of the author's knowledge, there currently exists no generative adversarial networks which aim to generate 3D facial models with speech audio as a conditional input.

### 2019-06-06 Report/Progress_Report/paper_summaries.tex
Finished section on data generation

\subsection{Audio-driven facial animation by joint end-to-end learning of pose and emotion}
I need to reread and take in depth notes on this.
This paper is more impressive than I initially gave it credit for.
Nvidia facial animation from speech \cite{Karras2017a}

@@

\subsection{Synthesising 3D Facial Motion from "In-the-Wild" Speech}
Read this again too.
Imperial Paper \cite{Tzirakis2019}

>>>>

\subsection{Audio-driven facial animation by joint end-to-end learning of pose and emotion}
Nvidia facial animation from speech \cite{Karras2017a}
Attempts to generate 3D facial animation from audio.
Output vertices difference from neutral face mesh.
Specific to actor, trained on 3-5 minutes of footage for that actor.
Model extracts temporal audio features with convolutional net.
Then convolutional net to analyse temporal components of speech.
Articulation network also accepts emotional state input to aim ambiguities between different facial shape from same audio.

@@

\subsection{Synthesising 3D Facial Motion from "In-the-Wild" Speech}
Model is independent of speaker and capture rig.
Create dataset by recording talking 4D faces speaking words from LRW dataset.
Register 3D meshes and learn 3D blendshapes.
Use DCAW to align speech with meshes to give ground truth.
Train a model to predict 3D facial motion from speech under uncontrolled conditions. 
Use audio from LRW dataset to train with.
Imperial Paper \cite{Tzirakis2019}
